Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-07-31 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:07:31	16:23:52	(Fri31.Jul)

\newpage
\section{Results and Discussion}

@@

\begin{figure*}\centering%
\includegraphics[width=\linewidth]{gfx/mvdr_selected_windows.eps}%
\caption{Typical window responses for a robust MVDR. The dashed red line is the response of an unsteered rectangular window on the full array. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3dB in highlight. The phase varies mostly in highlight. }\label{mvdr_selected_windows}
\end{figure*}

What's up?

@@

>>>>

\begin{figure*}[tbhp!]\centering%
\includegraphics[width=\linewidth]{gfx/mvdr_selected_windows.eps}%
\caption{Typical window responses for a robust MVDR. The dashed red line is the response of an unsteered rectangular window on the full array. Note how the responses are more or less symmetric, with very little steering in the shadow, moderate steering in speckle and steering within roughly 3dB in highlight. The phase varies mostly in highlight. Full opening angle. Parameters. }\label{mvdr_selected_windows}
\end{figure*}

\section{Results and Discussion}

The results from our LCA studies will be presented in the following order:

\begin{itemize}
\item \emph{Window function}. Studies of typical MVDR responses for shadow, speckle and highlight regions in an image.
\item \emph{Window parameters}. 
\end{itemize}

The following sections with expand and discuss these results further.

\subsection{Window function}

@@

While MVDR is free to choose non-symmetric windows, we can observe from \Fig{mvdr_selected_windows} that it prefers symmetric ones. In shadow and speckle the windows are fully symmetric, while in highlight the windows are approximately symmetric within the opening angle of the sonar.

@@

\subsection{Summary and order of results}

In short, our findings regarding the optimal window types for LCA is as follows:

\begin{itemize}
\item \emph{Window function} should be symmetric, . Studying typical MVDR responses for shadow, speckle and highlight regions, we believe it to be insignificant
\item \emph{Window parameters}. 
\end{itemize}

The following sections with expand and discuss these results further.
